%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.5 (01/05/24)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
% Modified for personal use by Joaquín (contact@jsoro.dev)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{developercv} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{white}{{\huge\textcolor{black}{\textbf{\MakeUppercase{Joaquín Soro}}}}} % First name
	
	\vspace{6pt}
	
	{\huge Software Engineer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Linkedin}{12}{\href{https://linkedin.com/in/jsoro}{jsoro (Linkedin)}}\\
	\icon{Globe}{12}{\href{https://jsoro.dev}{jsoro.dev (Website)}}\\
	\icon{Github}{12}{\href{https://github.com/j-soro}{github.com/j-soro}}\\
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{At}{12}{\href{mailto:contact@jsoro.dev}{contact@jsoro.dev}}\\	
	\icon{Phone}{12}{+34 680 601 004}\\
	\icon{MapMarker}{12}{Spain}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\vspace{0.5cm}
\begin{minipage}[t]{1\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
		\begin{itemize}
			\item I am \textbf{proactive \& passionate} with a \textbf{creative mindset} and a \textbf{resolutive attitude}.
			\item I \textbf{own my work} and love working \textbf{within a great team}, driven by \textbf{best practices}.
			\item I am \textbf{fluent in English (C1)} and \textbf{native in Spanish}, confident in conveying complex ideas.
			% \item Some hobbies: Nix, making music, D\&D, videogames, animals, nature/hiking, reading, cooking.
		\end{itemize}
% Dummy text
\end{minipage}
\hfill % Whitespace between
% \begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
% 	\vspace{-\baselineskip} % Required for vertically aligning minipages
% 	\begin{barchart}{5.5}
% 		\baritem{Data Engineering}{75}
% 		\baritem{Backend}{90}
% 		\baritem{Frontend}{50}
% 		\baritem{Cloud development}{70}
% 		\baritem{AI/ML}{65}
% 	\end{barchart}
% \end{minipage}

% \begin{center}
% 	\bubbles{5/Python, 4/ELK, 3/TS, 3/Cloud, 3/Linux, 3/Go}
% \end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{03/24 -- Current\\\footnotesize{remote, full time}}
		{Data Engineer / Go Software Engineer (Payments domain)}
		{Epos Now}
		{
			Contributed to the design, development and maintenance of a complex data platform.
			Engineered pipelines for report generation, monitoring and integrations. Engineered and developed new Go processes and refactored legacy C\# services.
			Led the adoption and development of an ETL orchestration platform using Airflow and refactored legacy pipelines into a modern, unified stack.
			\\
		\texttt{Go}\slashsep\texttt{C\#}\slashsep\texttt{PostgreSQL}\slashsep\texttt{Kafka}\slashsep\texttt{Airflow}
		\slashsep\texttt{Docker}\slashsep\texttt{Kubernetes}}
	
	\entry
		{06/23 -- 03/24\\\footnotesize{remote, full time}}
		{Data Engineer / Python \& Scala Engineer (Airlines domain)}
		{NEXT Digital (w. Iberia)}
		{
			Engineered and developed solutions using Scala, Spark, Kafka, ksqlDB in the AWS cloud stack.
			Migrated legacy processes and infrastructure towards Kafka stack. Designed and developed API services
			working with hexagonal architecture \& SOLID principles. Formed part of the operations/realtime data
			engineering platform for International Airlines Group. 
			\\
		\texttt{Kafka}\slashsep\texttt{ksqlDB}\slashsep\texttt{Airflow}\slashsep\texttt{PostgreSQL}\slashsep\texttt{Python}\slashsep\texttt{Scala}\slashsep\texttt{Docker}\slashsep\texttt{Kubernetes}}
	
	\entry
		{12/22 -- 06/23\\\footnotesize{remote, full time}}
		{Data Engineer (ELK) / Python Engineer (Banking Domain)}
		{Accenture (w. CaixaBank Tech)}
		{
			Engineered and improved an in-house complex data processing application.
			The processes involved different ingests and exports towards other outputs,
			dashboards, visualizations and documents.
			Microservice-based architecture which comprised data processing job
			definitions and scheduling.\\
		\texttt{Python}\slashsep\texttt{Elasticsearch}\slashsep\texttt{Kibana}
		\slashsep\texttt{Docker}\slashsep\texttt{Kubernetes}\slashsep\texttt{Consulting}}
	
	\entry
		{07/22 -- 12/22\\\footnotesize{full time}}
		{Junior Python Engineer - (AI SEO Startup, SaaS)}
		{Smartbrand (sb.digital)}
		{Developed features and participated in building a SaaS AI platform. The solution leveraged a complex, microservice-based architecture deployed in GCP. My roles involved the transition towards a Cloud-native, distributed, scalable, workflow-based rework parting from the initial MVP.\\
		\texttt{Python}\slashsep\texttt{Kafka}\slashsep\texttt{Redis}\slashsep\texttt{ELK}
		\slashsep\texttt{Kubernetes}\slashsep\texttt{Helm}\slashsep\texttt{GCP}\slashsep\texttt{MongoDB}}
	
	\entry
		{03/22 -- 06/22\\\footnotesize{full time}}
		{Junior Software Engineer Internship - (AI SEO Startup, SaaS)}
		{Smartbrand (sb.digital)}
		{Cooperated with team in delivering and testing features. Studied the project design and codebase. Generated reports and assessments to support development. \\ 
		\texttt{Python}\slashsep\texttt{Java}\slashsep\texttt{RabbitMQ}\slashsep\texttt{Git}\slashsep\texttt{Docker}\slashsep\texttt{Linux}\slashsep\texttt{MongoDB}\slashsep\texttt{Kubernetes}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2022 -- Current}
		{Bachelor's Degree, Software Engineering}
		{Universitat Oberta de Catalunya (https://uoc.edu)}
		{Currently studying software engineering in my free time. Computing and AI branch.}
	\entry
		{2020 -- 2022\\\footnotesize{>2000h}}
		{Higher Technical Expert in Application Development Degree}
		{(https://iespoetapacomolla.es)}
		{An in-depth higher degree of official professional education in backend development.}
	\entry
	{4/2022 -- 7/2023\\\footnotesize{>400h}}
	{Web Design And Development Bootcamp: Vue3 + Pinia}
	{Escuela de Organización Industrial (https://eoi.es)}
	{A JS/TS web/UX development course. I lead my team in developing an MVP for an accesibility-centered social media application. Vue3 + Firebase}
	\entry
		{3/2021 -- 7/2021\\\footnotesize{>600h}}
		{II Samsung Innovation Campus in AI, Deep Learning}
		{Universidad de Málaga (https://uma.es)}
		{A specialization course in Python, AI, Statistics and ML/DL. I built a Twitter emotion classifier web application for my final project. Featuring a LSTM deep learning model and dashboard reporting.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

% \begin{minipage}[t]{0.3\textwidth}
% 	\vspace{-\baselineskip} % Required for vertically aligning minipages

% 	\cvsect{Languages}
	
% 	\textbf{Spanish} - native\\
% 	\textbf{English} - fluent (C1)\\
% \end{minipage}
% \hfill
% \begin{minipage}[t]{0.7\textwidth}
% 	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
% 	% \cvsect{Hobbies}
	
	
% \end{minipage}

% \begin{minipage}[t]{0.7\textwidth}
% 	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
% 	\cvsect{Non profit}
	
% 	I help... \lorem
% \end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
